### 2018-07-06 paper/4-build.tex
Add reference to continuations

This approach requires that a task may be started and then suspended until
another task is complete. Suspending can be done with cheap green threads and blocking
(the original approach of \Shake) or using continuation-passing style (what
\Shake currently does).

>>>>

This approach requires that a task may be started and then suspended until
another task is complete. Suspending can be done with cheap green threads and blocking
(the original approach of \Shake) or using continuation-passing style \citep{claessen_continuations} (what
\Shake currently does).
